On Extending a Full-Sharing Multithreaded Tabling Design with Batched Scheduling

### 2015-05-26 paper.tex
paper -> revising 1

By observing Table~\ref{tab_batched_overhead}, we can see that, for 1
thread, on the minimum overhead ratio, local scheduling is better on
the NS design, while batched scheduling is better in the FS
design. For the average and maximum overhead ratios, in the FS design,
the best strategy is always the local scheduling.

As we scale the number of threads, for the NS design both scheduling
strategies have similar minimum, average and maximum overhead
ratios. For the FS design, the best minimum overhead ratio is always
for the batched scheduling. For the average and maximum overhead
ratio, local scheduling is always better than batched
scheduling. However, for the average ratio, the results between both
strategies is quite close. For the maximum overhead ratio, the
difference between both strategies is significantly higher.

%% As we scale the number of threads, one can observe that,
%% for the NS design both scheduling strategies have similar minimum,
%% average and maximum overhead ratios. For the FS design, the best
%% minimum overhead ratio on $1$, $8$, $16$, $24$ and $32$ threads is
%% always the batched scheduling. For the average and maximum overhead
%% ratio, local scheduling is always better than batched
%% scheduling. However, for the average ratio, the results between both
%% strategies is quite close. We consider this to be quite significant,
%% once the FS design with batched scheduling requires the support of the
%% PAC procedure. For the maximum overhead ratio, the difference between
%% both strategies is higher than for the average overhead ratio, however
%% we hope to reduce the difference with further improvements in the PAC
%% procedure.

>>>>

By observing Table~\ref{tab_batched_overhead}, we can see that, for 1
thread, on the minimum overhead ratio, local scheduling is better on
the NS design, while batched scheduling is better in the FS
design. For the average and maximum overhead ratios, in the FS design,
the best strategy is always the local scheduling. Additionally, the
difference between local and batched scheduling in the FS is higher
than in the NS design, which indicates the overhead that the PAC
strategy brings to the FS design. Recall, whenever an answer is found
during the evaluation, PAC requires threads to traverse their private
consumer data structures to check if the answer was already
propagated. This is the reason for overhead that we are observing in
the experimental results.

As we scale the number of threads, for the NS design both scheduling
strategies have similar minimum, average and maximum overhead
ratios. For the FS design, the best minimum overhead ratio is always
for the batched scheduling. For the average and maximum overhead
ratio, local scheduling is always better than batched
scheduling. However, for the average ratio, the results between both
strategies is quite close. For the maximum overhead ratio, the
difference between both strategies is significantly higher than in the
NS design.

In resume, the experimental results show that on average, the PAC
strategy does not seem to have a big impact in the performance,
however it still leaves room for further improvements, because the
difference between local and batched scheduling is higher in the FS
design than in the NS design.
